Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-26 introduction.tex
ongoing work in the introduction.

The Large Hadron Collider (LHC) was created to explore the fundamental
properties of matter for the next decades.  Since LHC start-up in 2009,
multiple experiments  at LHC have collected and distributed hundreds of
petabytes of data worldwide to hundreds of computer centers.
Thousands of physicists analyze petascale data volumes daily.
One of the LHC experiments, the ATLAS~\cite{Aad:2008}, utilizes the Production
and Distributed Analysis (PanDA) workload management system~\cite{Maeno2011}
(WMS) for distributed data processing and analysis. The ATLAS Computing
model~\cite{Atlas2005} is based on a Grid paradigm~\cite{Foster:1998}, with
multilevel, hierarchically distributed computing and storage resources. PanDA
has been developed to meet growing ATLAS production and analysis requirements
for a data-driven workload management system capable of operating at LHC data
processing scale.

@@

>>>>

The Large Hadron Collider (LHC) was created to explore the fundamental
properties of matter for the next decades.  Since LHC start-up in 2009,
multiple experiments  at LHC have collected and distributed hundreds of
petabytes of data worldwide to hundreds of computer centers. Thousands of
physicists analyze petascale data volumes daily. The detection of the Higgs
Boson speaks to the success of the detector and experiment design, as well as
the sophistication of computing systems devised to analyze the data.

Historically the computing systems consisted of the federation of a hundreds
to thousands of distributed resources \textemdash{} ranging in scale from
small to mid-size resource~\cite{foster2003grid}. Although the workloads to be
executed are independent, the management of the distribution of extremely-
large workloads across many heterogeneous resources to ensure the effective
utilization of resources and efficient execution of workloads presents non-
trivial challenges.

Many software solutions have been developed in response to these challenges.
One of the LHC experiments, the CMS experiment devised a solution based around
the HTCondor~\cite{XX} software ecosystem. The ATLAS~\cite{Aad:2008}
experiment, utilizes the Production and Distributed Analysis (PanDA) workload
management system~\cite{Maeno2011} (WMS) for distributed data processing and
analysis. The CMS and ATLAS experiments represent arguably the largest
production grade distributed computing solutions and have symbolized the
paradigm of {\it high-throughput computing} viz., the effective execution of
many independent workloads.

% Historically, the ATLAS Computing model~\cite{jones2008atlas} is based on a
% Grid paradigm~\cite{foster2003grid}, with multilevel, hierarchically
% distributed computing and storage resources.

% PanDA has been developed to meet
% growing ATLAS production and analysis requirements for a data-driven workload
% management system capable of operating at LHC data processing scale.

@@

\subsubsection*{The following is a candidate for major compression into a single paragraph}
